Evaluating 'Graphical Perception' with CNNs

### 2018-03-26 PAPER/03_elementary_perceptual_tasks.tex
Add the slim cross network graphic.

	\midrule
	\makecell[tl]{\emph{Position Non-Aligned Scale}} & \makecell[tl]{Origin\\+ Position Y\\+ Position X \\+ Spot Size \\} & \makecell[tr]{ $10$ \\$600$ \\ $36000$ \\ $216000$}\\

@@

	\midrule
	\makecell[tl]{\emph{Curvature}} & \makecell[tl]{Midpoint Curvature\\+ Position Y \\+ Position X\\+ Width} & \makecell[tr]{ $80$ \\ $1600$ \\ $64000$ \\ $2560000$}\\

	\midrule
	\makecell[tl]{\emph{Shading}} & \makecell[tl]{Density\\+ Position Y \\+ Position X} & \makecell[tr]{ $100$ \\ $1600$ \\ $2000$ \\ $40000$}\\

>>>>

	\midrule
	\makecell[tl]{\emph{Position Non-Aligned Scale}} & \makecell[tl]{Position Y\\+ Position X \\+ Spot Size \\} & \makecell[tr]{ $600$ \\ $36000$ \\ $216000$}\\

@@

	\midrule
	\makecell[tl]{\emph{Curvature}} & \makecell[tl]{Midpoint Curvature\\+ Position Y \\+ Position X} & \makecell[tr]{ $80$ \\ $1600$ \\ $64000$}\\

	\midrule
	\makecell[tl]{\emph{Shading}} & \makecell[tl]{Density\\+ Position Y \\+ Position X} & \makecell[tr]{ $100$ \\ $2000$ \\ $40000$}\\

### 2018-03-26 PAPER/07_results.tex
Add the slim cross network graphic.

\begin{figure}[t]
	  \includegraphics[width=\linewidth]{crossnetwork.pdf}
  \caption{\textbf{Cross-classifier variability for the perceptual task of measuring curvature.} We use predictions of LeNet classifiers trained on different parametrizations of the \emph{curvature} elementary perceptual task and measure the mean logistic absolute error (MLAE). The lower score, the better. Classifiers trained on curves with variable position can generalize even if the axis of translation varies. However, classifiers trained on fixed positions of curves are not able to measure translated curves.}
	\label{fig:cross_network}
\end{figure}

>>>>

\begin{figure}[t]
	  \includegraphics[width=\linewidth]{cross_network_small_VGG19.pdf}
  \caption{\textbf{Cross-classifier variability for the perceptual task of measuring length.} We use predictions of LeNet classifiers trained on different parametrizations of the \emph{curvature} elementary perceptual task and measure the mean logistic absolute error (MLAE). The lower score, the better. Classifiers trained on curves with variable position can generalize even if the axis of translation varies. However, classifiers trained on fixed positions of curves are not able to measure translated curves.}
	\label{fig:cross_network}
\end{figure}
